Psychological Science Submission Letter

### 2023-03-27 paper/admin/cover_letter.tex
udpated cover letter

\documentclass[10pt,stdletter,orderfromtodate,sigleft]{newlfm}
\usepackage{blindtext, xfrac, animate, hyperref, pxfonts}

@@

\newlfmP{dateskipbefore=0pt}
\newlfmP{sigsize=20pt}
\newlfmP{sigskipbefore=10pt}

@@

\namefrom{Jeremy R. Manning, Ph.D.}
\addrfrom{
	Dartmouth College\\
  Department of Psychological \& Brain Sciences\\
  HB 6207 Moore Hall\\
	Hanover, NH  03755}

\addrto{}
\dateset{\today}

\greetto{To the editors of \textit{Scientific Reports}:}

@@

As we anticipated, participants in both conditions remembered stimuli they
attended to better than unattended stimuli, and they rated both attended and
unattended stimuli they had seen as more ``familiar'' than novel images, during
a recognition memory test. We also found some interesting differences across
the two experimental conditions pertaining to how participants remembered
``partially attended'' stimuli. When participants varied the focus of their
attention more often, their memory was more influenced by location-based
attention (regardless of which image category they were attending). In
contrast, when participants sustained the focus of their attention over longer
intervals, their memory was more influenced by category-based attention
(regardless of which location they were attending). Our findings highlight a
dissociation between how location-based and category-based attention affect
memory encoding (and subsequent recognition). Location-based attention appears
to affect memory encoding on relatively short timescales by enhancing encoding
for stimuli at the attended location. On the other hand, category-based
attention appears to affect memory encoding on longer timescales by
\textit{suppressing} stimuli from the unattended category.

The impact of attention on memory is of central importance to a wide
variety of scientifically and socially current issues.  For example,
the interplay between attention and memory affects how we remember our
ongoing experiences in everyday life, how students learn in the
classroom (and which teaching strategies might be most effective), how
(or whether) we recognize a face we notice in a crowd and
happen to encounter later, and so on.  These issues also relate to
attention disorders (e.g., ADD, ADHD) and memory disorders
(e.g., age-related memory impairment, Alzheimer's, etc.).  Discovering
the mechanisms that underlie how our experiences are encoded into
memories can lead to new tools for identifying when those mechanisms
are not operating within their expected parameters.

We have suggested the following scientists as expert reviewers: Marvin Chun
(Marvin.Chun@Yale.edu), Brice Kuhl (bkuhl@uoregon.edu), Joel Voss
(Joel-Voss@Northwestern.edu), Edward Vogel (Ed\-Vogel@UChi\-ca\-go.edu), and
Judith Fan (jefan@ucsd.edu). We have also published and documented all of our
experimental stimuli, code, and data, along with the code used to generate the
figures and analyses we report in our manuscript. These may be found at
\href{https://github.com/ContextLab/attention-memory-task}{\texttt{https://github.com/ContextLab/attention-memory-task}}.

Thank you for considering our manuscript for publication in
Psychonomic Bulletin \& Review.

>>>>

\documentclass[10pt,stdletter,orderfromtodate,sigleft]{newlfm}
\usepackage{blindtext, xfrac, animate, hyperref, pxfonts}
\usepackage[subtle]{savetrees}

@@

\newlfmP{dateskipbefore=0pt}
\newlfmP{sigsize=10pt}
\newlfmP{sigskipbefore=10pt}

@@

\namefrom{Jeremy R. Manning, Ph.D.}
\addrfrom{}

\addrto{}
\dateset{}

\greetto{\vspace{-1in}To the editors of \textit{Scientific Reports}:}

@@

As we had expected, participants in both conditions remembered stimuli they
attended to better than unattended stimuli, and they rated both attended and
unattended stimuli they had seen as more ``familiar'' than novel images, during
a recognition memory test. In addition, we also found some interesting
(unexpected) differences across the two experimental conditions pertaining to how
participants remembered ``partially attended'' stimuli. When participants
varied the focus of their attention more often, their memory was more
influenced by location-based attention (regardless of which image category they
were attending). In contrast, when participants sustained the focus of their
attention over longer intervals, their memory was more influenced by
category-based attention (regardless of which location they were attending).
Our findings highlight a dissociation between how location-based and
category-based attention affect memory encoding (and subsequent recognition).
Location-based attention appears to affect memory encoding on relatively short
timescales by enhancing encoding for stimuli at the attended location. On the
other hand, category-based attention appears to affect memory encoding on
longer timescales by \textit{suppressing} stimuli from the unattended category.

The impact of attention on memory is of central importance to a wide variety of
scientifically and socially current issues. For example, the interplay between
attention and memory affects how we remember our ongoing experiences in
everyday life, how students learn in the classroom (and which teaching
strategies might be most effective), how (or whether) we recognize a face we
notice in a crowd and happen to encounter later, and so on. These issues also
relate to attention disorders (e.g., ADD, ADHD) and memory disorders (e.g.,
age-related memory impairment, Alzheimer's, etc.). Discovering the processes
that guide how our experiences are encoded into memories can lead to new tools
for identifying when those processes are not operating within their expected
parameters.

In the spirit of reproducibility and transparency, we have also published and
documented all of our experimental stimuli, code, and data, along with the code
used to generate the figures and analyses we report in our manuscript. These
may be found at
\href{https://github.com/ContextLab/attention-memory-task}{\texttt{https://github.com/ContextLab/attention-memory-task}}.

Thank you for considering our manuscript for publication in \textit{Scientific Reports}.
